\textcolor[rgb]{0,0,1}{Data-Driven Model Predictive Control using Random Forests for Building Energy Optimization and Climate Control}

### 2018-01-23 paper/final/Response_to_reviewers/Response_to_reviewers.tex

	\item \textbf{Editor:} \textit{An updated and complete literature review should be conducted.}

	\textbf{Authors:} We conducted and updated and complete literature review. In particular, in Table 1 we classify the related work and then emphasize the novelty of our research with respect to each prior work.

	\item \textbf{Editor:} \textit{The relevance to Applied Energy should be enhanced with the considerations of scope and readership of the Journal. The present form has little relevance to APEN which might suit better for another journal. Authors must address and enhance the relevance to Applied Energy otherwise, they can consider to publish in another journal.}

	\textbf{Authors:} In the initial submission we had chosen a more general title and discussion in the introduction because we believe that our approach has the potential to be applied not only to building management, but also to other application domains. However, as in this paper we develop our techniques focusing and experimenting in building management we changed the title in ``Data-Driven Model Predictive Control using Random Forests for Building Energy Optimization and Climate Control" and re-wrote the introduction of the paper focusing on the relevance of the paper contribution to building energy management, bridging machine learning and control for energy flexibility.\\\\
	Now that we better emphasized the relevance of the paper to building energy management, and since "\textit{Applied Energy provides a forum for information on innovation, research, development and demonstration in the areas of energy conversion and conservation, the optimal use of energy resources, analysis and optimization of energy processes, mitigation of environmental pollutants, and sustainable energy systems" (https://www.journals.elsevier.com/applied-energy)}, we really hope that our paper will be considered relevant to APEN, especially with respect to the topics "\textit{optimal use of energy resources}" and "\textit{analysis and optimization of energy processes}". We also hope that our paper will be considered related to the APEN keywords \textit{Energy efficiency and energy saving: strategies, applications and implications}, \textit{Energy system analysis, simulation and modeling}, \textit{Implementation of energy R\&D strategies and policies}, \textit{Energy system and automation} and \textit{Sustainable buildings}.

@@

	\item \textbf{Editor:} \textit{A proof reading by a native English speaker should be conducted to improve both language and organization quality.}

	\textbf{Authors:} We thoroughly revised and proofread the paper to improve both language and organization quality.

@@

	\item \textbf{Editor:} \textit{The originality of the paper needs to be further clarified. The present form does not have sufficient results to justify the novelty of a high quality journal paper. The results should be further elaborated to show how they could be used for the real applications.}

	\textbf{Authors:} In the ``Related work" and ``Main contribution" subsections of the Introduction, we clarified the novelty of the paper with respect to existing results and emphasized the contributions provided.\\

		In the newly added Section 2, we highlighted the typical drawbacks of the model-based approaches, which limit the use of advanced control techniques for energy optimization such as MPC due to the difficulties (cost, time and effort) related to the model creation, and show how the data-driven approach that we propose (DPC) overcomes these limitations.\\

		In Sections 4,5 and 6 we show how our DPC methodology can be used for real applications. In particular, in Section 4 we demonstrate that DPC can provide comparable performance with respect to classical MPC applied to a perfectly known mathematical model. In Section 5, we apply DPC to a 6 story 22 zone building model in EnergyPlus, for which model-based control is not economical and practical due to extreme complexity, and address a Demand Response problem. Our results demonstrate scalability and efficiency of DPC showing that it provides the desired power curtailment with an average error of 3\%. In Section 6 we implement and test DPC on real data from an off-grid house located in L'Aquila, Italy. We compare the total amount of energy saved with respect to the classical bang-bang controller, showing that DPC can perform an energy saving up to $49.2\%$. We also demonstrate the robustness of our method to uncertainties both in real data acquisition (affected by unpredictable house schedules due to people, appliances, etc., noisy sensor measurements due to real experimental data, etc.) and weather forecast.
\end{enumerate}

@@

\item \textbf{Reviewer 1:} \textit{In Section 2.1, what is the relationship between these training features and labels $(X^c, X^d, Y)$ and the input, output, disturbance, and state variables in the traditional state space model? Are they the same?}

\textbf{Authors:} We thank the reviewer for this comment, indeed this very important part of the paper was not clear in the initial submission. We added a new section (Section 2) where we reported a traditional physics-based state-space modeling of a building (Section 2.1) and compared it with the data-driven modeling approach (Section 2.2). We highlighted the differences in the modeling techniques and emphasized that the features needed in the data-driven approaches are ALL and ONLY the measurable variables (hence a subset of all the variables) used in the model-based approach, since the model learning procedure is able to compensate the effect of the non-measurable variables. This is also further discussed in Section 3, where we added more mathematical details to make the presentation more clear and rigorous.

\item \textbf{Reviewer 1:} \textit{Another point is that in traditional state space model, one cannot measure everything except input and output in most cases. How could we obtain such training data if these data are not measurable.}

\textbf{Authors:} We thank the reviewer for this comment, indeed our previous presentation of the paper was unclear on this fundamental aspect, we apologize for this. In our revision we clearly illustrate in Section 2, how in traditional state-space models part of the state is measurable (i.e. room temperatures, etc) and part is not measurable (i.e. layers/windows temperatures, time of day, day of week, holidays, etc). In our approach, of course, $(\mathcal{X}, \mathcal{Y})$ are ALL measurable variables, i.e. variables that are present in the historical dataset of a building. The unmeasurable variables of the traditional state-space models are not assumed to be measurable in this paper, yet our prediction works well since we (implicitly) account for their effect via the regression tree/random forest approaches.

@@

\item \textbf{Reviewer 2:} \textit{The paper applies a recently developed concept, data predictive control (DPC) to building energy control. Models based on decision trees and random forests are applied. The efficacy of the approach appears well validated.}

\textbf{Authors:} We thank the Reviewer for the comment on our validation of the efficacy of our approach.

\item \textbf{Reviewer 2:} \textit{The title is a bit confusing as it's very general. It should be changed to be more specifically focusing on the applications in this paper.}

\textbf{Authors:} We agree with the Reviewer. In the initial submission we had chosen a more general title (and discussion in the introduction) because we believe that our approach has the potential to be applied not only to building energy management, but also to other application domains. However, as in this paper we develop our techniques focusing and experimenting in building management (which is indeed a core topic of APEN), we changed the title to "Data-Driven Model Predictive Control using Random Forests for Building Energy Optimization and Climate Control" (and re-wrote the introduction of the paper focusing on the relevance of the paper contribution to building energy management).

@@

\item \textbf{Reviewer 2:} \textit{Also, novelties beyond what's in [9] - [12] should be clarified.}

\textbf{Authors:} In subsection "1.1 Related work" of the revised version we discuss in detail the novelty of our paper beyond [9,10,11,12] (which are numbered [25,26,31,32] in the revised version). We summarize the novel contributions of our paper in the initial paragraph of subsection "1.2 Main contribution":
\textit{In this paper, we provide a new methodology based on random forests that overcomes the drawbacks of all our previous works, and more precisely: we obtain better performance and scalability when compared to other approaches (both optimal and rule-based), and we provide and validate robustness with respect to uncertainties due to real data acquisition and weather forecast inaccuracies.}
After the above paragraph in the paper, we describe our contributions in detail.

@@

\textbf{Authors:} We thank the reviewer for rising this important issue. As discussed in the previous answer, in this revision we re-wrote Section 3 and improved the description of the main optimization problems. Answering to the specific questions of the reviewer: yes, as we look ahead to do DPC, each future time slot has a different linear model, depending on future non-manipulative disturbances; yes, we assume that, at time $k$, we know the future non-manipulative disturbances (namely external temperature, radiation, etc.) for the Model Predictive Control time horizon. In the revised version of this paper, to justify this assumption, we first provide a reference paper [57] that investigates the effect of uncertainty in the weather forecast on the performance of MPC in building systems operations through a large-scale simulation study, and compares against a rule-based strategy. They consider 48 different scenarios of uncertainties for 72 hours weather forecast. With such a long horizon, results have shown that (with a few exceptions) MPC outperforms the rule-based controller in providing energy savings, and is in general quite close to the perfect forecast case despite the uncertainty in weather forecast. Since the length of horizon for the DPC algorithm presented in this paper is usually much shorter, for example $6$ hours in Section 4, $7$ hours in Section 5, and $40$ minutes in Section 6, we can reasonably presume that our approach will be robust to weather forecast inaccuracies. In our opinion, robustness of DPC to weather forecast inaccuracies is due to 2 main features:

	\begin{itemize}

	\item weather forecasts, are in general, quite accurate on a short-term horizon;

@@

	\end{itemize}
	Finally, in Section 6 we add a new subsection where we test the robustness of our approach by perturbing the weather forecast with Gaussian noises with large variance. The results show that the control performance is indeed very close to the ideal case even with a large error in the weather forecast.

\item \textbf{Reviewer 2:} \textit{In Fig. 6b, what's the difference between blue and yellow, as they seem to completely overlap?}

\textbf{Authors:} We have clarified this point in the text and the Figure caption. In particular, marked in blue is the response when the optimal input is applied to the power predictive model of the Random Forest and in red is the response when the same input is applied to the power predictive model of EnergyPlus. Since the optimal input is computed using the power predictive model of the Random Forest, the blue trajectory perfectly follows the tracking signal. The red trajectory, as expected, is characterised by a (small) tracking error because of the model mismatch between the predictive model of the Random Forest (used to compute the input) and that of EnergyPlus (used to simulate the closed-loop system).

\item \textbf{Reviewer 2:} \textit{Also, what is new in section 5 compared with section 4? Even though a real house is claimed to be used, it's still tested using simulations and EnergyPlus, like in the previous sections. A real world experiment on this house would be much more interesting.}

@@

\textbf{Authors:} We thank the reviewer for this comment, indeed the contribution of Section 6 (i.e. Section 5 in the initial submission) was not well emphasized. We now emphasize the difference between Section 5 (i.e. Section 4 in the initial submission) and Section 6 (i.e. Section 5 in the initial submission):
\begin{itemize}

	\item As the main difference, in Section 5 we use the EnergyPlus model both to create the predictive model via Random Forests and to test the DPC performance. Although the EnergyPlus model is quite accurate, it still provides simulated data, that differs from real experimental data, which does not suffer from non-predictable imperfections such as random occupancy schedules, open/close windows, random light on/off switch, etc. In Section 6, instead, real data is used to build the Random Forests models, while the EnergyPlus model (created ad-hoc for the house) is ONLY used to compare the total amount of energy can be saved applying DPC with respect to the classical bang-bang controller.
